\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{margin=1in}

\title{Chapter 1.5 - Exercise Solutions}
\author{Fay Huang \\ NIU Department of CSIE}
\date{}

\begin{document}

\maketitle

\section*{1. Find an elementary matrix $F$ that satisfies the stated equation.}

\[
F = \begin{bmatrix}
8 & 1 & 5 \\
8 & 1 & 1 \\
3 & 4 & 1
\end{bmatrix}
\]

\noindent $F$ was obtained from $B$ by adding 2 times the third row to the second row.

\section*{2. Find the inverse of the $4 \times 4$ matrix, where $k_1, k_2, k_3, k_4$ are all nonzero.}

The identity matrix was adjoined to the given matrix.

\begin{itemize}
  \item The first and fourth rows were interchanged.
  \item The second and third rows were interchanged.
  \item The rows were scaled respectively by $\frac{1}{k_1}, \frac{1}{k_2}, \frac{1}{k_3}, \frac{1}{k_4}$.
\end{itemize}

\noindent The inverse is a diagonal matrix with entries $\frac{1}{k_i}$ on the diagonal, after proper row swaps.

\section*{3. Suggested Exercises}

\begin{enumerate}
  \item Find a row operation and the corresponding elementary matrix that will restore the given elementary matrix to the identity matrix.

  \[
  \text{(a)} \quad
  \begin{bmatrix}
  1 & 0 & 0 \\
  9 & 1 & 0 \\
  -5 & 0 & 1
  \end{bmatrix}
  \]

  Add 5 times the first row to the third row.

  \item Find an elementary matrix $E$ such that $EB = A$.

  \item Use the inversion algorithm to find the inverse of the matrix (if the inverse exists).

  \[
  A = \begin{bmatrix}
  1 & 2 & 3 \\
  2 & 5 & 3 \\
  1 & 0 & 8
  \end{bmatrix}
  \]

  The inverse is:

  \[
  A^{-1} = \frac{1}{-40}
  \begin{bmatrix}
  13 & -5 & ? \\
  ? & ? & ? \\
  ? & ? & ?
  \end{bmatrix}
  \]
  \textit{(Incomplete in original image)}
\end{enumerate}

\section*{4. Find all values of $c$, if any, for which the given matrix is invertible.}

\[
\begin{bmatrix}
1 & 0 \\
c & 1 \\
1 & c
\end{bmatrix}
\]

Apply row operations and check for linear dependence.

\section*{5. Express the matrix and its inverse as products of elementary matrices.}

\section*{6. Show that a given matrix is not invertible for any values of the entries.}

\end{document}
